---
title: "Poll Paper"
author: "Keene Morrow"
date: "5/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(janitor)
library(here)
library(RColorBrewer)
```

Gallup Poll. March 1-8, 2018. N=1,041 adults nationwide. Margin of error ± 4.

"Do you think the U.S. government is doing too much, too little, or about the right amount in terms of protecting the environment?"
```{r}
poll <- read.csv("poll.csv") %>% 
  janitor::clean_names()

poll_long <- poll %>%
  pivot_longer(cols = 4:7,
               names_to = "position",
               values_to = "percent")

ggplot(data = poll_long) +
  geom_area(aes(x = year,
                y = (100*percent),
                fill = position))
```




"Next, I am going to read some specific proposals. For each one, please say whether you generally favor or oppose it. How about . . . ?"
"Passing a carbon tax to encourage reductions in carbon dioxide emissions"
```{r}
carbon <- read.csv("carbon_long.csv") %>% 
  janitor::clean_names()

ggplot(data = carbon) +
  geom_col(aes(x = position,
               y = percent,
               fill = position),
           show.legend = FALSE) +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Public Opinion on:",
       subtitle = "Passing a carbon tax to encourage reductions in carbon dioxide emissions",
       x = "Position",
       y = "Percent",
       caption = "Gallup Poll. March 1-8, 2018. N=1,041 adults nationwide. Margin of error ± 4\n\nESM 243: Spring 2021\nKeene Morrow") +
  theme_minimal() +
  theme(plot.caption = element_text(hjust = 0, face = "italic"))
```



